Can money buy happiness?

### 2022-04-29 draft2.Rmd
Added alt text!

```{r}
GDPP_hours <- healthy_data_2 %>% 
ggplot( aes(x = GDPPC, y = `Hours Worked`, fill = `City`)) +
  geom_point(color = "#3C1518") +
  labs(title = "Gross Domestic Product per Capita by Country and Average Weekly Hours Worked",
       caption = "Data from: ADD LATER",
       x = "GDP per capita (USD)",
       y = "Hours Worked (Weekly)",
       color = "") +
  theme(legend.position = "none",
        panel.background = element_rect(fill = "#FFE5B4",
                                colour = "gray",
                                size = 0.5,
                                ),
        plot.title = element_text(size = 0.05))

>>>>

```{r, width = 800, fig.alt="This graph shows the relationship between GDP per capita and the number of weekly hours worked in each city. The GDPC is represented along the x axis, and the number of hours worked is arranged in increasing order along the y axis. When hovering over each individual point, the corresponding city, GDP per capita, and number of hours worked is revealed in a small textbox."}

GDPP_hours <- healthy_data_2 %>% 
ggplot( aes(x = GDPPC, y = `Hours Worked`, fill = `City`)) +
  geom_point(color = "#3C1518") +
  labs(title = "Gross Domestic Product per Capita by Country and Average Weekly Hours Worked",
       x = "GDP per capita (USD)",
       y = "Hours Worked (Weekly)",
       caption = "Data from: Healthy Lifestyle Cities Report 2021, IMF World Economic Outlook",
       color = "") +
  theme(legend.position = "none",
        panel.background = element_rect(fill = "#FFE5B4",
                                colour = "gray",
                                size = 0.5,
                                ),
        plot.title = element_text(size = 0.05))
